Integrated approach to modeling to krill population dynamics in Wester Antarctic Peninsula: spatial and ecosystem considerations

### 2024-10-08 index.Rmd
adding test new test files

@@

```{r fig.height=6}
SSplotSelex(base.model01,
            subplots = 1)
SSplotSelex(base.model1,
            subplots = 1)
SSplotSelex(base.model2,
            subplots = 1)
SSplotSelex(base.model3,
            subplots = 1)
SSplotSelex(base.model4,
            subplots = 1)
SSplotSelex(base.model5,
            subplots = 1)
SSplotSelex(base.model6,
            subplots = 1)
SSplotSelex(base.model7,
            subplots = 1)
```
```{r}
SSplotComps(base.modeltest,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
```

>>>>

Just some time series plots

```{r}
SSplotTimeseries(base.modeltest,
                 subplot = 1)
SSplotTimeseries(base.modeltest,
                 subplot = 9)
```
and fits

```{r}
SSplotComps(base.modeltest,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
```

@@

```{r fig.height=6}
SSplotSelex(base.model01,
            subplots = 1)
SSplotSelex(base.model1,
            subplots = 1)
SSplotSelex(base.model2,
            subplots = 1)
SSplotSelex(base.model3,
            subplots = 1)
SSplotSelex(base.model4,
            subplots = 1)
SSplotSelex(base.model5,
            subplots = 1)
SSplotSelex(base.model6,
            subplots = 1)
SSplotSelex(base.modeltest,
            subplots = 1)
```
